Deciding to Disclose

### 2015-11-16 article.tex
Renaming sections

The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}). 
\section{Disclosure Game Model}
\label{sec:model}

>>>>

The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:midwives_model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}). 
\section{Disclosure Game Model}
\label{sec:midwives_model}
